Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-13 paper/paper.tex
Unnecessary word which starts a new line

For both subgraph isomorphism and maximum common subgraph, constraint programming is the best known
approach\footnote{Note that toolkits are not used in state of the art implementations, to facilitate
better memory layouts and propagation queues, although the algorithms are heavily inspired by
constraint programming.}, although a reduction to maximum clique is better when edge labels are
present \citep{DBLP:conf/cp/NdiayeS11,DBLP:conf/cp/McCreeshNPS16}. For both problems, we create a variable for each vertex
in the pattern graph (the smaller graph, in the case of maximum common subgraph), with domains
ranging over the vertices in the target graph (the larger graph). For maximum common subgraph, each
domain is given an additional $\bot$ value, meaning ``unmapped''.

>>>>

For both subgraph isomorphism and maximum common subgraph, constraint programming is the best known
approach\footnote{Note that toolkits are not used in state of the art implementations, to facilitate
better memory layouts and propagation queues, although the algorithms are inspired by
constraint programming.}, although a reduction to maximum clique is better when edge labels are
present \citep{DBLP:conf/cp/NdiayeS11,DBLP:conf/cp/McCreeshNPS16}. For both problems, we create a variable for each vertex
in the pattern graph (the smaller graph, in the case of maximum common subgraph), with domains
ranging over the vertices in the target graph (the larger graph). For maximum common subgraph, each
domain is given an additional $\bot$ value, meaning ``unmapped''.
